How do we copy and paste? The semantic drift of quotations in blogspace

### 2015-03-05 brains-protocol.tex
APAize enumerations

\begin{itemize}
    \item \textbf{Word frequency}: the frequency at which words appear in our dataset, known to be relevant for both recognition and recall~\citep{gregg1976word},
    \item \textbf{Age of Acquisition}: the average age at which words are learned (obtained from~\citet{Kuperman12}), known to have different effects than word frequency~\citep{morrison1995roles,dewhurst1998separate},
    \item The average \textbf{Number of Phonemes} and \textbf{Number of Syllables} for all pronunciations of a word (obtained from the Carnegie Mellon University Pronouncing Dictionary~\citep{Weide98})\footnote{The CMU Pronouncing Dictionary is included in the NTLK package~\citep{Bird09}, the natural language processing toolkit we used for the analysis.} as a proxy to word production cost,
    \item The average \textbf{Number of Synonyms} for all meanings of a word (obtained from \citet{WordNet10}) as an \emph{a priori} indicator of how easy it would be to replace a word.
\end{itemize}

@@

\begin{itemize}
    \item \textbf{Degree centrality}, measured by the number of cues for which a given word is triggered as a target, and a corresponding generalized measure, node \emph{pagerank}~\citep{Page99}, which has already been used on the FA network by~\citet{Griffiths07}.
    In the present case these two polysemy-related measures are quasi-perfectly correlated. %, and measure polysemy by taking into account the structure of the entire network.
    %However in the present case there is a quasi-perfect correlation between node incoming degree and node \emph{pagerank}~\citep{Page99}, which will lead us to favour the latter later on. Word pagerank on the FA network had already been used by~\citet{Griffiths07}; it may be interpreted as a generalized and recursive measure of word polysemy: central nodes in the pagerank sense are words often selected as targets when presented with cues themselves often selected as targets, and so on recursively.
    \item \textbf{Betweenness centrality}, another measure of node centrality describing the extent to which a node connects otherwise remote areas of the network~\citep{free:set}.
    This quantity tells us if some words behave like unavoidable waypoints on association chains connecting one word to another.
    \item \textbf{Clustering coefficient}, which measures the extent to which a node belongs to a local aggregate of tightly connected nodes~\cite{watt-coll}, computed on the undirected version of the FA network.\footnote{The Clustering coefficient is formally defined as the ratio between the number of actual vs. possible edges between a node's neighbors.}
    This tells us if a word belongs more or less to a local aggregate of equivalent words (from a ``free association'' point of view).
\end{itemize}

@@

This approach yields a fine-grained view of how word features evolve upon substitution, on average, with respect to (i) the original feature (\hbox{vs.} $y=x$) and (ii) a random arrival (\hbox{vs.} $\nu_{\phi}^0$).
\begin{figure*}[!th]
    \centering
    \includegraphics[width=\textwidth]{images/computed-figures/feature_variations-binned.png}
    \caption{\textbf{Feature variation upon substitution:} $\nu_\phi$, average feature value of the appearing word as a function of the feature value of the disappearing word in a substitution, with 95\% asymptotic confidence intervals.
    The overall position of the curve with respect to the dashed line representing $\mathcal{H}_0$ (constant $\nu_{\phi}^0$) indicates the direction of the cognitive bias.
    The intersection with $y = x$ marks the attractor value.
    %The fact that all curves have slopes smaller than 1 means that the substitution operation is contractile on average: each feature will converge towards its own specific asymptotic range.    
    }
    \label{fig:feature-variations}
\end{figure*}

\medskip
Results are gathered in Fig.~\ref{fig:feature-variations}.
We can do a first striking observation: all graphs show the existence of a unique intersection of $\nu_{\phi}$ with $y=x$, while the slope of $\nu_{\phi}$ is smaller than 1, independently of the feature considered.
In other words, beyond individual variation patterns, the substitution process is contractile for all the features, and each of them therefore exhibits a unique attractor.
Second, the comparison with $\nu_{\phi}^0$ shows that there are two classes of attractors, depending on whether:
\begin{enumerate}[(i)] 
\item there is a triple intersection (of $y=x$, $\nu_{\phi}^0$ and $\nu_{\phi}$);
\item or $\nu_{\phi}$ always remains above or below $\nu_{\phi}^0$.
\end{enumerate}
The first class (Number of phonemes and Number of synonyms) are features for which the substitution process only brings words slightly closer to $\nu_{\phi}^0$, and no uniform bias can be observed.
%\TB{(furthermore, $\mathcal{H}_{00}$ stays inside the confidence intervals of $\nu_{\phi}$, confirming that these two features are irrelevant for the substitution process)}.
%\rk{Cam: On vire ou bien?}

>>>>

\begin{APAitemize}
    \item \textbf{Word frequency}: the frequency at which words appear in our dataset, known to be relevant for both recognition and recall~\citep{gregg1976word},
    \item \textbf{Age of Acquisition}: the average age at which words are learned (obtained from~\citet{Kuperman12}), known to have different effects than word frequency~\citep{morrison1995roles,dewhurst1998separate},
    \item The average \textbf{Number of Phonemes} and \textbf{Number of Syllables} for all pronunciations of a word (obtained from the Carnegie Mellon University Pronouncing Dictionary~\citep{Weide98})\footnote{The CMU Pronouncing Dictionary is included in the NTLK package~\citep{Bird09}, the natural language processing toolkit we used for the analysis.} as a proxy to word production cost,
    \item The average \textbf{Number of Synonyms} for all meanings of a word (obtained from \citet{WordNet10}) as an \emph{a priori} indicator of how easy it would be to replace a word.
\end{APAitemize}

@@

\begin{APAitemize}
    \item \textbf{Degree centrality}, measured by the number of cues for which a given word is triggered as a target, and a corresponding generalized measure, node \emph{pagerank}~\citep{Page99}, which has already been used on the FA network by~\citet{Griffiths07}.
    In the present case these two polysemy-related measures are quasi-perfectly correlated. %, and measure polysemy by taking into account the structure of the entire network.
    %However in the present case there is a quasi-perfect correlation between node incoming degree and node \emph{pagerank}~\citep{Page99}, which will lead us to favour the latter later on. Word pagerank on the FA network had already been used by~\citet{Griffiths07}; it may be interpreted as a generalized and recursive measure of word polysemy: central nodes in the pagerank sense are words often selected as targets when presented with cues themselves often selected as targets, and so on recursively.
    \item \textbf{Betweenness centrality}, another measure of node centrality describing the extent to which a node connects otherwise remote areas of the network~\citep{free:set}.
    This quantity tells us if some words behave like unavoidable waypoints on association chains connecting one word to another.
    \item \textbf{Clustering coefficient}, which measures the extent to which a node belongs to a local aggregate of tightly connected nodes~\cite{watt-coll}, computed on the undirected version of the FA network.\footnote{The Clustering coefficient is formally defined as the ratio between the number of actual vs. possible edges between a node's neighbors.}
    This tells us if a word belongs more or less to a local aggregate of equivalent words (from a ``free association'' point of view).
\end{APAitemize}

@@

This approach yields a fine-grained view of how word features evolve upon substitution, on average, with respect to 
\begin{seriate}
\item the original feature (\hbox{vs.} $y=x$) and 
\item a random arrival (\hbox{vs.} $\nu_{\phi}^0$).
\end{seriate}
\begin{figure*}[!th]
    \centering
    \includegraphics[width=\textwidth]{images/computed-figures/feature_variations-binned.png}
    \caption{\textbf{Feature variation upon substitution:} $\nu_\phi$, average feature value of the appearing word as a function of the feature value of the disappearing word in a substitution, with 95\% asymptotic confidence intervals.
    The overall position of the curve with respect to the dashed line representing $\mathcal{H}_0$ (constant $\nu_{\phi}^0$) indicates the direction of the cognitive bias.
    The intersection with $y = x$ marks the attractor value.
    %The fact that all curves have slopes smaller than 1 means that the substitution operation is contractile on average: each feature will converge towards its own specific asymptotic range.    
    }
    \label{fig:feature-variations}
\end{figure*}

\medskip
Results are gathered in Fig.~\ref{fig:feature-variations}.
We can do a first striking observation: all graphs show the existence of a unique intersection of $\nu_{\phi}$ with $y=x$, while the slope of $\nu_{\phi}$ is smaller than 1, independently of the feature considered.
In other words, beyond individual variation patterns, the substitution process is contractile for all the features, and each of them therefore exhibits a unique attractor.
Second, the comparison with $\nu_{\phi}^0$ shows that there are two classes of attractors, depending on whether:
\begin{APAenumerate} 
\item there is a triple intersection (of $y=x$, $\nu_{\phi}^0$ and $\nu_{\phi}$);
\item or $\nu_{\phi}$ always remains above or below $\nu_{\phi}^0$.
\end{APAenumerate}
The first class (Number of phonemes and Number of synonyms) are features for which the substitution process only brings words slightly closer to $\nu_{\phi}^0$, and no uniform bias can be observed.
%\TB{(furthermore, $\mathcal{H}_{00}$ stays inside the confidence intervals of $\nu_{\phi}$, confirming that these two features are irrelevant for the substitution process)}.
%\rk{Cam: On vire ou bien?}
